Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-17 paper/results.tex
Latest.

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots are available as supplemental material due to reasons of space.

@@

\paragraph{Selection oracle.} As expected, the selection oracle yields the best performance on all datasets. Fig.~\ref{fig:ac4trails} shows VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$). With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1600$ corrections. With guided proofreading, the oracle reaches a minimum median VI of $0.342$ ($SD=0.03$) after $800$ corrections. Both results are close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires fewer corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods. On the L.~Cylinder dataset (initial VI $0.379$, $SD=0.118$), focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted). Guided proofreading reduces the median VI to $0.2996$ ($SD=0.073$) after $27,491$ corrections ($2,696$ accepted).

>>>>

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Please note that additional plots are available as supplemental material due to reasons of space.

@@

\paragraph{Selection oracle.} As expected, the selection oracle yields the best performance on all datasets. Fig.~\ref{fig:ac4trails} shows VI reduction using the selection oracle on the AC4 subvolume (initial median VI $0.476$, $SD=0.089$). With focused proofreading, the selection oracle reaches a median VI of $0.353$ ($SD=0.037$) after $1600$ corrections. With guided proofreading, the oracle reaches a minimum median VI of $0.342$ ($SD=0.03$) after $800$ corrections. Both results are close to the best possible median VI of $0.334$ (calculated by computing maximum overlap with the ground truth). The slope of the trails in Fig.~\ref{fig:ac4trails} shows that guided proofreading requires fewer corrections to reach a reasonable reduction in VI. Fig.~\ref{fig:ac4boxplot} shows the VI distribution across methods. On the L.~Cylinder dataset (initial VI $0.379$, $SD=0.118$), focused proofreading reduces the median VI to $0.298$ ($SD=0.075$) after $26,170$ corrections ($2,419$ accepted). Guided proofreading reaches the minimum median VI $0.2996$ ($SD=0.073$) after $10,000$ corrections (in total $27,491$, $2,696$ accepted).
